### 2024-03-22 doc/15yrsChange.Rmd
adding data objects to the rmarkdown

#5 Year Averages for top three species

#Peak for each species
```

>>>>

avg_fram <- allmort_awm %>% filter(sp == "fram") %>% pull(abgmort) %>% 
  mean(na.rm = TRUE)
avg_quve <- allmort_awm %>% filter(sp == "quve") %>% pull(abgmort) %>% 
  mean(na.rm = TRUE)
avg_quru <- allmort_awm %>% filter(sp == "quru") %>% pull(abgmort) %>%
  mean(na.rm = TRUE)
avg_qupr <- allmort_awm %>% filter(sp == "qupr") %>% pull(abgmort) %>% 
  mean(na.rm = TRUE)
avg_qual <- allmort_awm %>% filter(sp == "qual") %>% pull(abgmort) %>% 
  mean(na.rm = TRUE)
avg_litu <- allmort_awm %>% filter(sp == "litu") %>% pull(abgmort) %>% 
  mean(na.rm = TRUE)
avg_other <- allmort_awm %>%  mutate(plot_species = if_else(sp %in% top_sp$sp,sp, "Other")) %>% filter(plot_species == "Other") %>% pull(abgmort) %>% mean(na.rm = TRUE)

#5 Year Averages for top three species -- Currently calculated with survey_years 2014-2023

avg_fram_first5 <- allmort_awm %>% filter(sp == "fram" & (survey_year == "2014" | survey_year == "2015" | survey_year == "2016" | survey_year == "2017" | survey_year == "2018")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

avg_fram_second5 <- allmort_awm %>% filter(sp == "fram" & (survey_year == "2019" | survey_year == "2020" | survey_year == "2021" | survey_year == "2022" | survey_year == "2023")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

avg_quve_five5 <- allmort_awm %>% filter(sp == "quve" & (survey_year == "2014" | survey_year == "2015" | survey_year == "2016" | survey_year == "2017" | survey_year == "2018")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

avg_quve_second5 <- allmort_awm %>% filter(sp == "quve" & (survey_year == "2019" | survey_year == "2020" | survey_year == "2021" | survey_year == "2022" | survey_year == "2023")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

avg_quru_first5 <-  allmort_awm %>% filter(sp == "quru" & (survey_year == "2014" | survey_year == "2015" | survey_year == "2016" | survey_year == "2017" | survey_year == "2018")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

avg_quru_second5 <- allmort_awm %>% filter(sp == "quru" & (survey_year == "2019" | survey_year == "2020" | survey_year == "2021" | survey_year == "2022" | survey_year == "2023")) %>% pull(abgmort) %>% mean(na.rm = TRUE)

#Peak for each species

fram_peak <-  allmort_awm %>% filter(sp == "fram") %>% pull(abgmort) %>% max(na.rm = TRUE)

quve_peak <- allmort_awm %>% filter(sp == "quve") %>% pull(abgmort) %>% max(na.rm = TRUE)

quru_peak <- allmort_awm %>% filter(sp == "quru") %>% pull(abgmort) %>% max(na.rm = TRUE)

qupr_peak <- allmort_awm %>% filter(sp == "qupr") %>% pull(abgmort) %>% max(na.rm = TRUE)

qual_peak <- allmort_awm %>% filter(sp == "quru") %>% pull(abgmort) %>% max(na.rm = TRUE)

litu_peak <- allmort_awm %>% filter(sp == "litu") %>% pull(abgmort) %>% max(na.rm = TRUE)

other_peak <- allmort_awm %>%  mutate(plot_species = if_else(sp %in% top_sp$sp,sp, "Other")) %>% filter(plot_species == "Other") %>% pull(abgmort) %>% max(na.rm = TRUE)

##Figure 5

#Total number of recruits in canopy and understory for each region

#Canopy
group1_canopy <- plotdf %>% filter(Group == "1" & canopy_position == "canopy")%>% pull(n_stems) %>% sum(na.rm = TRUE)
group2_canopy <- plotdf %>% filter(Group == "2" & canopy_position == "canopy")%>% pull(n_stems) %>% sum(na.rm = TRUE)
group3_canopy <- plotdf %>% filter(Group == "3" & canopy_position == "canopy")%>% pull(n_stems) %>% sum(na.rm = TRUE)

#Understory
group1_understory <- plotdf %>% filter(Group == "1" & canopy_position == "understory")%>% pull(n_stems) %>% sum(na.rm = TRUE)
group2_understory <- plotdf %>% filter(Group == "2" & canopy_position == "understory")%>% pull(n_stems) %>% sum(na.rm = TRUE)
group3_understory <- plotdf %>% filter(Group == "3" & canopy_position == "understory")%>% pull(n_stems) %>% sum(na.rm = TRUE)

#Number of recruits for oak spp, hickory spp, libe and astr in each of the groups

#Oak recruits
group1_oakRecruit <- plotdf %>% filter(Group == "1" & plot_sp == "Quercus spp.")%>% pull(n_stems)
group2_oakRecruit <- plotdf %>% filter(Group == "2" & plot_sp == "Quercus spp.") %>% pull(n_stems)
group3_oakRecruit <- plotdf %>% filter(Group == "3" & plot_sp == "Quercus spp.")%>% pull(n_stems)

#Hickory Recruits
group1_hickoryRecruit <- plotdf %>% filter(Group == "1" & plot_sp == "Carya spp.")%>% pull(n_stems)
group2_hickoryRecruit <- plotdf %>% filter(Group == "2" & plot_sp == "Carya spp.")%>% pull(n_stems)
group2_hickoryRecruit <- plotdf %>% filter(Group == "3" & plot_sp == "Carya spp.")%>% pull(n_stems)

#libe Recruits
group1_libeRecruit <- plotdf %>% filter(Group == "1" & plot_sp == "Lindera benzoin") %>% pull(n_stems)
group2_libeRecruit <- plotdf %>% filter(Group == "2" & plot_sp == "Lindera benzoin") %>% pull(n_stems)
group3_libeRecruit <- plotdf %>% filter(Group == "3" & plot_sp == "Lindera benzoin") %>% pull(n_stems)

#astr Recruits
group1_astrRecruit <- plotdf %>% filter(Group == "1" & plot_sp == "Asimina triloba") %>% pull(n_stems)
group2_astrRecruit <- plotdf %>% filter(Group == "2" & plot_sp == "Asimina triloba") %>% pull(n_stems)
group3_astrRecruit <- plotdf %>% filter(Group == "3" & plot_sp == "Asimina triloba") %>% pull(n_stems)
